---
title: "READme"
output: github_document

 
---

# Overview/Purpose

Practical on…

The following code was used to create the workspace environment:

```{r, eval=FALSE}

fmxdat::make_project(FilePath="/Users/tiagob/Documents/Masters 2021/First Semester/Data Science/DS Assessment 1",ProjNam='19776209')

Texevier::create_template(directory='/Users/tiagob/Documents/Masters 2021/First Semester/Data Science/DS Assessment 1/19776209/', template_name= 'Question 1')
Texevier::create_template(directory='/Users/tiagob/Documents/Masters 2021/First Semester/Data Science/DS Assessment 1/19776209/', template_name= 'Question 2')
Texevier::create_template(directory='/Users/tiagob/Documents/Masters 2021/First Semester/Data Science/DS Assessment 1/19776209/', template_name= 'Question 3')

```

# Question 1 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
library(pacman)
pacman::p_load(tidyverse, jtools, Hmisc)
if(!require(lubridate)) library(lubridate)

gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.

	#loading data from CSV
df_mov <- read.csv("/Users/tiagob/Documents/Masters 2021/First Semester/Data Science/Assessment_NK/19776209/Question 1/data/Movies.csv")

```

## Summary Statistics

The dataset used to investigate the above claims is sourced from an associate at Mr Video, and contains info on movie critic and grossing data; with 74 observations in 8 variables. Statistics on the variables were generated using: 

``` {r, evaluate=FALSE}

describe(df_mov)

```

Describe how to answer; what function is doing.

```{r}

Sumfun <- …

```
For tables/plots.
```{r, message=FALSE}

Function for output

```
\newpage

# Question 2 

## Solution

\newpage

# Question 3 

## Solution